Appendix B

### 2021-03-31 manuscript/appendix_B.Rmd
re-run

```{r}
# K is at twice max of f3; 8 * K_3 / 5
f1 <- function(x, h = 0, r = 2, K = 10 * 8 / 5){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}
f2 <- function(x, h = 0, r = 0.5, K = 10){
  s <- pmax(x - h, 0)
  s + s * (r * (1 - s / K) )
}

# max is at 4 * K / 5 
f3  <- function(x, h = 0, r = .002, K = 10){
  s <- pmax(x - h, 0)
  s + s ^ 4 * r * (1 - s / K)
}
```

@@

## gather models together, indicate true model
sigma_g <- 0.05
models <- c(f3, models)
model_sigmas <- c(sigma_g, pars$sigma)
true_model <- 1
```

@@

@@

```{r plot_models, fig.width=6, fig.height=4}
model_set <- models
names(model_set) <- c("true", 1:n_models)
d <- 
  map_dfc(model_set, function(f) f(states) - states) %>%
  mutate(state = states)

@@

@@

Passive adaptive management using a Bayesian learning scheme still learns the wrong model.

```{r}
adaptive_management <- memoise::memoise(mdp_learning, cache = memoise::cache_filesystem("cache/"))
x0 <- which.min(abs(states - 6))
## start with 90% weight on 'model 1'
model_prior <- c(rep(.1, length(models)-2) / (length(models) - 2), .9)

am_many <- adaptive_management(transitions[-1],  
                           reward = reward, 
                           discount = discount,
                           model_prior = model_prior,
                           x0 = x0, 
                           Tmax = 20, 
                           true_transition = transitions[[true_model]], 
                           epsilon = 0.001, 
                           max_iter = 2000)
```

@@

```{r}
policy <- mdp_compute_policy(transitions[-1],  
                           reward = reward, 
                           discount = discount,
                           model_prior = model_prior,
                           Tmax = 20)
non_adaptive <- memoise::memoise(mdp_planning, cache = memoise::cache_filesystem("cache/"))
x0 <- which.min(abs(states - 6))
## start with 90% weight on 'model 1'
model_prior <- c(rep(.1, length(models)-2) / (length(models) - 2), .9)

non_am <- non_adaptive(transitions[-1],  
                           reward = reward, 
                           discount = discount,
                           model_prior = model_prior,
                           x0 = x0, 
                           policy = policy,
                           Tmax = 20, 
                           true_transition = transitions[[true_model]], 
                           epsilon = 0.001, 
                           max_iter = 2000)
```

>>>>

```{r}
# max is at 4 * K / 5 
f3  <- function(x, h = 0, r = .002, K = 10){
  s <- pmax(x - h, 0)
  s + s ^ 4 * r * (1 - s / K)
}
```

@@

## gather models together, indicate true model
sigma_g <- 0.05
model_sigmas <- pars$sigma
```

@@

true_transition <- transition_matrices(f3, states, actions, sigma_g)
```

@@

```{r plot_models, fig.width=6, fig.height=4}
model_set <-c(f3,  models)
names(model_set) <- c("true", 1:length(models))
d <- 
  map_dfc(model_set, function(f) f(states) - states) %>%
  mutate(state = states)

@@

# Non-adaptive management over model uncertainty

With strong prior probabilities weighted to Model 1

```{r}
x0 <- which.min(abs(states - 6))
## start with 99% weight on 'model 1'
model_prior <- c(rep(.01, length(models)-1) / (length(models) - 1), .99)

```{r}
policy_sdp <- memoise::memoise(mdp_compute_policy, cache = memoise::cache_filesystem("cache/"))

policy <- policy_sdp(transitions,  
                     reward = reward, 
                     discount = discount,
                     model_prior = model_prior,
                     Tmax = 20, 
                     epsilon = 0.001, 
                     max_iter = 2000)

policy %>% mutate(state = states[state], quota = actions[policy]) %>% mutate(escapement = state - quota) %>% ggplot(aes(state, escapement)) + geom_line()
```

```{r}

non_am <- mdp_planning(true_transition,  
                       reward = reward, 
                       discount = discount,
                       model_prior = model_prior,
                       x0 = x0, 
                       a0 = 1,
                       policy = policy$policy,
                       Tmax = 20)

non_am %>% mutate(state = states[state]) %>% ggplot(aes(time, state)) + geom_point() + geom_line()

@@

Passive adaptive management, with initial strong prior probabilities weighted to Model 1.

```{r}
adaptive_management <- memoise::memoise(mdp_learning, cache = memoise::cache_filesystem("cache/"))

am_many <- adaptive_management(transitions,  
                           reward = reward, 
                           discount = discount,
                           model_prior = model_prior,
                           x0 = x0, 
                           Tmax = 20, 
                           true_transition = true_transition, 
                           epsilon = 0.001, 
                           max_iter = 2000)
```

@@
